---
title: "Lab 8"
output: html_document
name: Vic
student number: 24283699
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```
#Question 1
```{r}
sd <- read.csv("sensor.csv")
head(sd, 20)

sd2 <- na.omit(sd)
sd3 <- subset(sd2, value >= 0)
sensors_clean <- subset(sd3, value <= 100)

mylist <- list(
  nrow(sensors_clean),
  min(sensors_clean$value),
  mean(sensors_clean$value),
  range(sensors_clean$value),
  max(sensors_clean$value, sensors_clean$sensorid == 2),
  length(subset(sensors_clean, siteid == 1, sensorid == 2))
)

mylist

qplot(sensors_clean$value, geom="histogram",fill=I("green"), col=I("black"), xlab = "Sensor Value", main = "Histogram of Sensor Values") 

boxplot(sensors_clean$value ~ sensors_clean$sensorid, xlab = "Sensor ID", ylab = "Reading", main = "Sensor Values by Sensor")
```

#Question 2

###H0:µ < 45
###HA:µ >= 45
```{r}
t.test(sensors_clean$value, mu = 45, alternative = "greater")
```
### Fail to reject null hypothesis. There is insufficient evidence to conclude that the mean value of all sensors is not less than 45. (P > 0.05)

#Question 3

###H0:mean(new_data1$value) !=  mean(new_data2)
###HA:mean(new_data1$value) ==  mean(new_data2)
```{r}
new_data <- subset(sensors_clean, siteid == 1 || siteid == 2)
new_data1 <- subset(new_data, siteid == 1)
new_data2 <- subset(new_data, siteid == 2)
t.test(new_data1$value,new_data2$value)
```
### Fail to reject null hypothesis. There is insufficient evidence to conclude that the mean value new_data1 != to mean value new_data2. (P > 0.05)

#Question 4
```{r}
advertising <- read.csv("advertising.csv")
tail(advertising, 15)

plot(advertising$Radio, advertising$Sales) 
plot(advertising$TV, advertising$Sales) 
plot(advertising$Newspaper, advertising$Sales) 

linmod <- lm(advertising$Sales ~ advertising$TV)
linmod
summary(linmod)

plot(advertising$TV, advertising$Sales) 
abline(linmod)
```